\boldmath Commissioning of the highly granular SiW-ECAL technological prototype

### 2018-08-20 performance-paper-draft/longversion/draft.tex
All changes implemented. One last revision missing.

\abstract{
  High precision physics at future colliders as the International Linear Collider (ILC) require unprecedented high precision in the determination
  of the final state of the particles produced in the collissions
  The needed precision will be achieved thanks to the Particle Flow algorithms (PF) which require compact, highly granular and hermetic calorimeters systems.
  The Silicon-Tungsten Electromagnetic Calorimeter (SiW-ECAL) technological prototype
  design and R\&D is oriented at the baseline design of the ECAL of the International Large Detector (ILD) for the ILC.
  In this article we present the commissioning and the performance of the prototype in our beam test carried at DESY in June 2017.
}

@@

Future accelerator based particle physics experiments
require very precise and detailed reconstruction of the final states produced
in the beam collisions. A particular example is the next generation of $e^{+}e^{-}$
linear colliders such the ILC\cite{Behnke:2013xla,Baer:2013cma,Adolphsen:2013jya,Adolphsen:2013kya,Behnke:2013lya}.
This project will provide collisions of polarized beams with centre-of-mass energies ($c.m.e$) of 250 GeV - 1 TeV.
These collisions will be studied by two multipurpose detectors:
the International Large Detector (ILD) and the Silicon Detector (SiD)\cite{Behnke:2013lya}.
To meet the precision levels required by the ILC %or CLIC
physics goals,
new techniques relying on single particle separation to make possible the choice of the best information available
in the full detector to measure the energy of the final state objects have been developed.
These techniques are called Particle Flow (PF) techniques \cite{Brient:2002gh,Morgunov:2004ed,Sefkow:2015hna}
and allow to reduce the impact of the poor resolution of the calorimeter systems (compared with trackers) in the overall reconstruction.
The PF algorithms impose some special requirements in the design of the detectors.
For example, it requires highly granular, compact
and hermetic calorimeters.

The CALICE collaboration is driving most of the efforts on R\&D of highly granular calorimeters \cite{Sefkow:2015hna} 
for future linear colliders by investigating and building prototypes for several
calorimeter concepts. One of these calorimeters 
is the silicon-tungsten electromagnetic calorimeter, SiW-ECAL.
The SiW-ECAL is the baseline choice for the ILD electromagnetic calorimeter.
It consists of a detector (in the barrel region) of 24 $X_{0}$ of thickness which corresponds to $\sim 1~\lambda_{I}$ (interaction length).
It has silicon (Si) as active material and tungsten (W) as absorber material.
The combination of Si and W choices  makes possible the design and construction
of a very compact calorimeter with highly granular and compact active layers.
It will be built an alveolar structure of carbon fiber into which modules made of tungsten
plates and the active sensors will be inserted. The very-front-end (VFE) electronics will be
embedded in the detector units. The silicon sensors will be segmented
in squared cells (or channels) of 5x5 mm: a total of $\sim 100$ million readout channels will constitute the ECAL for ILD.
The desired signal dynamic range in each channel goes from 0.5 MIP to 3000 MIPs.
To reduce overall power consumption, the SiW-ECAL will exploit the special bunch structure
foreseen for the ILC: the $e^{+}e^{-}$ bunchs trains will arrive in spills
of $\sim$ 1-2 ms width separated by $\sim$ 200 ms. The data acquisition will be gated during these short windows and during the idle time the bias currents of the electronics will be shut down.
This technique is usually denominated power pulsing. In addition to this, to cope with the large amount of channels,
the calorimeters should work in self-trigger mode (each channel featuring an internal trigger decision chain) and zero suppression mode.

@@

The current prototype is called the SiW-ECAL technological prototype. It addresses the main technological challenges: compactness,
power consumption reduction through power pulsing and VFE inside the detector close to real ILD conditions.
It will also provide data to deeply study the PF and provide input to tune simulation programs as for example
GEANT4\cite{Agostinelli:2002hh,Allison:2006ve,Allison:2016lfl} which is widely used
in particle physics to simulate the passage of particles through matter. In this section we described in detail
the main features and characteristics of the technollogical prototype.

@@

Current version of the PCB is called the FEV11. It has a thickness of 1.6mm and 2.7mm
if we include on top the ASICs in its current packaging (1.1 mm thick LFBGA package).
With these characteristics, a potential density of
3800 channels/dm$^{3}$ is achievable keeping the space and
interaction length requirements of the the baseline design of the ECAL forthe ILD.
This number should be compared with
the density achieved in beam tests with the physics prototype: 1500 channels/dm$^{3}$.
With the first versions
of the technollogical prototype we reached similar potential density level as in
the current version but equipping only a
quarter of the ASUs surface \cite{Amjad:2014tha}.

@@

A photograph showing the SiW-ECAL technollogical prototype setup can be seen in Figure \ref{proto}.
Current prototype consists on 7 layers of SLABs housed by a PVC and aluminum structure that can hold up to 10, in slots separated by 15mm each.
The first six layers were placed in the first six slots and the last one was in the last slot. In the following sections, we will refer to layers number 1 to 7, where
the 1 is the closest to the beam pipe and 7 is the farthest.
This setup is used for commissioning (Section \ref{sec:commissioning}) and for the beam test
(Section \ref{sec:beamtest}). In both cases, the detector was
running in power pulsing mode.

@@

All runs dedicated to the commissioning were characterized by:
\begin{itemize}
  \item their short gating windows for the acqusition (1-2ms)
   at low repetition frequencies (1-5 Hz) to minimize the chances of having real events due to cosmic rays during the data taking and the coherent noise events due to grounding issues;
 \item and the relatively high trigger threshold values between 400 and 250 DAC 
(which are equivalent to $\sim$2 and $\sim$0.5 MIP respectively, see Section \ref{sec:comm_trigger} for more information).
\end{itemize}

@@

We found to different types of noisy channels. One set consists of
channels randomy distributed along the surface of every ASU and the oter consists
of channels systematically noisy in all the ASUs. Preliminary inspections of the PCB layout
hint that the channels in the latter set are noisy due to
improvable routing of the PCB.
Deeper studies on the PCB routing must be conducted to clarify this.
All the noisy channels have been identified and masked and the power
of their preamplifiers has beem disabled. All the results shown in the following
sections are obtained in these conditions.

The list of the noisy channels was
obtained by means of dedicated data taking runs. In these runs
we scan trigger thresholds and progressively mask channels that exhibit counts. 
In each step, the decission of tagging a channel as noisy was taking following the next rules:

@@

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
  \includegraphics[width=4in]{../figs/commissioning/masked_layer.eps} \\
  \includegraphics[width=4in]{../figs/commissioning/masked_chip.eps}
  \end{tabular}
\caption{Fraction of channels that are tagged as noisy in all slabs. 
Top: inventory of the different type of noisy channels per slab. 
Bottom: break down of the total number of noisy channels per ASIC. 
The ASICs 4-7 (wafer issue) and 10 from layer 1 and the ASIC 4 from layer 7 are not included
in the second plot since they are fully masked.}
\label{noisycells}
\end{figure}

@@

After the noisy channels have been masked, dedicated trigger threshold
scan run are taken, and the results are shown in threshold scan curves where the
x-axis represents the threshold value\footnote{The threshold values are given in internal DAC units which are translated to
meaningful physical quantities in Section \ref{sec:comm_trigger_sn}.} and the y-axis
the number of recorded signals normalized to 1.
In the absence of external signals (cosmic rays, injected signals, etc) 
the falling edge position in the threshold scan curves
is due to the electronic noise
at the output of the fast shaper (the trigger decision branch on the SKIROC)
and it depends on the slow clock frequency.
These threshold scan curves are approximated by a complementary error function:

\begin{equation}
\frac{2p_{0}}{\sqrt(\pi)} \int_{\frac{DAC-p_{1}}{p_{2}}}^{\infty} e^{-t^{2}} dt,
\label{eq_S-curve}
\end{equation}
where $p_{0}$ is 1/2 of the normalization, $p_{1}$ is the value in which the noise levels are 
the 50\% of its maximum and $p_{2}$ give us the width of the ThS curve.

@@

For every ASICs, after performing the fit of the theoretical curves
to the threshold scans, the average values of the   $p_{1}$ and $p_{2}$ are calculated.
These are represented by $<p_{1,2}^{ASIC}>$ in the following.
The final threshold value of every ASIC, in DAC units, was chosen 
using the following formula
\begin{equation}
DAC_{optimal}^{ASIC} =maximum(<p_{1}^{ASIC}> + 5 \times <p_{2}^{ASIC}>,230).
\end{equation}
This formula was applied 
if at least the the 30\% of the 64 channels in the ASIC could be fitted.
If not, a global DAC value of 250 was set.

@@

\begin{figure}[!t]
    \centering
  \begin{tabular}{l}
	\includegraphics[width=4in]{../figs/commissioning/scurve_pp_fastshaper_ch.eps} \\
	\end{tabular}
\caption{Threshold scan curves with charge injection (1 MIP in blue and 2 MIPs in red) for two different channels in a SKIROC2 testboard.}
\label{scurves_injection}
\end{figure}

@@

Using this new procedure we manage to reduce the number of masked channels by a factor of two
without any loss of performance, at least in the laboratory and using 3 of the 7 SLABs.
This new procedure will alo be applied in the next beam test.
Also, in order to
optimize the commissioning of the detector,
we propose a new set of measurements in the next beam test such as
a threshold scan for the determination of the S/N in the trigger line. The later
can be done by the comparison of threshold curves taken with incident MIP-acting particles
and MIP-acting particles traversing the detector tilted by 45 degrees with respect to the beam direction.

\section{Performance on positron beam test at DESY}
\label{sec:beamtest}

The beam test line at DESY provides continuous positron beams in the energy range of 1 to 6 GeV with
rates from few hundreds of Hz to few KHz with a maximum of $\sim 3$ KHz for 2-3 GeV. 
The particles beam ies produced as follows: first, the electron/positron synchrotron DORIS II 
is used to produced a photon beam via bremsstralhung when interacting with a carbon fiber target;
secondly, these photons are then converted to electron/positron pairs; 
and, finally, the beam energy is selected with dipole magnets and collimators. 
In addition, DESY gives acces to a bore 1 T solenoid, the PCMag.

@@

\begin{enumerate}
\item Calibration without tungsten absorber using 3 GeV positrons acting as minimum ionizing particle (MIPs) directed to 81 position equally distributed over the modules.
\item Test in magnetic field up to 1 T using the PCMag. For this test a special PVC structure was
designed and produced to support one single SLAB.	
The purpose of such test was twofold: first to prove that the DAQ, all electronic devices and the 
mechanical consistency of the SLAB itself are able
to handle strong magnetic fields; 
second to check the quality of the data and the performance of the detector during the data taking when running
in a magnetic field.
\item Response to electrons of different energies with fully equipped detector, i.e. sensitive parts {\it and} W absorber, with three different repartitions of the absorber material:
\begin{itemize}
\item W-configuration 1: $0.6,1.2,1.8,2.4,3.6,4.8$ and $6.6~X_{0}$
\item W-configuration 2: $1.2,1.8,2.4,3.6,4.8,6.6$ and $8.4~X_{0}$
\item W-configuration 3: $1.8,2.4,3.6,4.8,6.6,8.4$ and $10.2~X_{0}$
\end{itemize}
\end{enumerate}

First reports on this beam test can be find in
Refs. \cite{Irles:2018uum,Irles:2018hcd}. In this paper we discuss in more detail
the results of the pedestal, noise and MIP calibration in Section \ref{sec:calib}.
We show also results on the pedestal and noise stability when running inside
a magnetic field in Section \ref{sec:magnet}. Finally, a first peek to the 
response and stability of the detector in electromagnetic showers events is discussed in 
Section \ref{sec:showers}.

\subsection{Response to MIP-acting positrons}
\label{sec:calib}

The calibration runs have been used to calculate the pedestal distribution reference values 
and the noise levels (the width of the pedestal distrution) of each channel.
In Figure \ref{signal_pedestal} we show the signal and pedestal distribution of a single channel after
subtracting the pedestal mean position. The results of the MIP calibration fit are shown in red (see Section \ref{sec:mip} for more details)
The pedestal distribution is shown only for the first SCA to keep the y-axis within a reasonable range.
The signal distribution is integrated over all SCAs.

\subsubsection{Pedestal and noise determination}
\label{sec:pedestal}

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
    \includegraphics[width=4in]{../figs/mip_pedestal_example.eps}
  \end{tabular}
  \caption{Pedestal (blue dashed line) and signal (black continuous line) distribution for one channel in the third layer.}
\label{signal_pedestal}
\end{figure}

The pedestal is calculated as the mean position of
the ADC distribution of channels without trigger. The noise is
associated to the width of such distribution.
The pedestal correction is done layer-, chip-, channel- and SCA-wisely due to the large spread of values between pedestals, as observed in 
Figure \ref{pedestal_layer} (left plot) and Figure \ref{pedestal_all} (also left plot).
For the noise, the dispersion is much smaller ($\sim 5 \%$). This is shown in the right plots of Figures \ref{pedestal_layer} and \ref{pedestal_all}.
From now on, the pedestal correction is applied to all the results presented.

%\begin{figure}[!t]
%  \centering
%  \begin{tabular}{ll}
%    \includegraphics[width=2.8in]{../figs/pedestal/ped_mean_layer2_chip4_cell10.eps} & \includegraphics[width=2.8in]{../figs/pedestal/ped_width_layer2_chip4_cell10.eps}
%  \end{tabular}
%  \caption{Pedestal mean position (left) and width (right) for one channel in the second layer.}
%\label{pedestal_channel}
%\end{figure}

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
    \includegraphics[width=2.8in]{../figs/pedestal/ped_mean_layer2.eps} & \includegraphics[width=2.8in]{../figs/pedestal/width_mean_layer2.eps}
  \end{tabular}
  \caption{Pedestal mean position (upper plot) and width (lower plot) for all channels in one layer. The data is grouped on bunches in which the value in the x-axis
    corresponds to the value of the channel number plus the value of the ASIC number multiplied by 100. The black points show the value for the first SCA
    and the red points show the average value for all the others SCAs (with the standard deviation of the sample as error bar).}
\label{pedestal_layer}
\end{figure}

@@

\subsubsection{Energy calibration and tracking efficiency}
\label{sec:mip}

After the pedestals are calculated and subtracted to the hit distributions, those are fit by
a Landau function convoluted with a Gaussian.
The most-probable-value of the convoluted function is taken as the MIP value, allowing thus for a direct
conversion from ADC units to energy in MIP units.
We have obtained a raw energy calibration spread of the 5\% among all channels with the 98\% of all 
available channels being fitted. Results are summarized in figure \ref{mipandSN}, leftmost plot.

@@

We checked the MIP 
calibration in all callibrated channels by selecting tracks
incident perpendicullary to the layers surface.
The results are shown in figure \ref{mip3peaks} where the single channel energy 
distribution for MIPs is shown for all calibrated channels in the same distribution. 
The maximum peaks at 1 MIP as expected after a good calibration.
In addition to this, a second and a third peak
appear visible. These peaks are due to
events involving multiple 
particles crossing the detector.

\begin{figure}[!t]
  \centering 
    \begin{tabular}{ll}
      \includegraphics[width=4in]{../figs/MIP/MIP3peaks.eps} 
    \end{tabular}
    \caption{Energy distribution for all callibrated channels when selecting tracks of 3 GeV positron acting as MIPs.}
\label{mip3peaks}
\end{figure}

To evaluate 
the single hit detection efficiency we define a high purity sample of
events by selecting
tracks with at least 4 layers with a hit in exactly the same channel. Afterwards we 
check if the other layers have or not a hit in the same channel (expanding the search
to the closest neighbouring channels) with energy larger or equal than 0.3 MIP.
Finally, we repeat this for all layers 
and channels. The results are shown in Figure \ref{efficiency}. Except few exceptions, the efficiency is 
compatible with $100\%$.
Lower efficiencies in the first layer are related to the presence of
noisy channels not spotted during the commissioning. In the last layer (separated from the
other layers by four slots of 1.5 cm instead of only one) we also observe few small deviations
from the $\sim100\%$ which are indeed
associated to a slight misalignment of the detector.
If we remove these channels from the analysis
the full efficiency is recovered.

\begin{figure}[!t]
  \centering 
    \begin{tabular}{ll}
      \includegraphics[width=2.8in]{../figs/MIP/efficiency_nhits4_chips.eps} & \includegraphics[width=2.8in]{../figs/MIP/efficiency_nhits4_chips_zoom.eps} \\
    \end{tabular}
    \caption{Left: MIP detection efficiency for all layers and ASICs in high purity samples of tracks of MIP-like acting particles. Right: same figures with a zoom in the y-axis. In both cases, the average efficiency of the 64 channels in each ASIC is shown.}
\label{efficiency}
\end{figure}

@@

The signal-over-noise ratio in the charge measurement (corresponding to the slow shaper of the SKIROC2) is defined 
as the ratio between the most-probable-value of
the Landau-gauss function fit to the data (pedestal subtracted) and the noise (the pedestal width). This quantity 
has been calculated for all channels and all layers. The average S/N is to 20.4.
Results are summarized in Figure \ref{mipandSN}, rightmost plot.

@@

The data taking inside the magnetic field has been divided in three steps:
a) a with a magnetic field of 1 T; b) a run with 0.5 T; c) a final run with the magnet off.
The beam, 3 GeV positrons, was hitting in the area of the PCB readout by the ASIC number 12.

The pedestal positions and noise levels of the channels of the ASIC 12 when the
SLAB is inside of the PCMag are compared with the results from the calibration run described in the previous section.
This is shown in Figure \ref{pedestal_magnetic}.
We see that the agreement is perfect within the statistical uncertainties.
Due to the lower rates in this beam area, the
analysis is only done up to few SCAs.

@@

In this section we discuss the pedestal stability in events with large amount of charge collected by the ASICs, as are the 
electromagnetic shower events. All the results shown in this section correspond to data taken during the tungsten program, 
using the W-configuration number 2 when shooting the beam in the area registered by the ASIC 12 (and partially in the 13). 
Only information recorded by ASIC 12 is used in the analysis. For other configurations we get comparable results.
In order to select a high purity of
electromagnetic shower like the events, 
we used a simple criteria: select only events with at least 6 of the layers with at least a hit with E > 0.5 MIP.

\begin{figure}[!t]
  \centering 
    \begin{tabular}{ll}
      \includegraphics[width=2.8in]{../figs/pedestal/pedestal_vs_energy_shower.eps} & \includegraphics[width=2.8in]{../figs/pedestal/pedestal_vs_nhits_shower.eps} \\
    \end{tabular}
    \caption{Left: mean position of the projection of the pedestal distribution of all channels
      calculated when different energies are collected in the ASIC (in bins of 10 MIPs).
      Right: same but as a function of the number of hits. In both cases, the results are shown for few SCA.
      The points for the curves with SCA larger than zero are slightly shifted in the x-axis to optimize the visualization.}
\label{pedestal_shower_1}
\end{figure}

>>>>

\abstract{
  High precision physics at future colliders as the International Linear Collider (ILC) require unprecedented high precision in the determination
  of the final state of the particles produced in the collisions
  The needed precision will be achieved thanks to the Particle Flow algorithms (PF) which require compact, highly granular and hermetic calorimeters systems.
  The Silicon-Tungsten Electromagnetic Calorimeter (SiW-ECAL) technological prototype
  design and R\&D is oriented at the baseline design of the ECAL of the International Large Detector (ILD) for the ILC.
  In this article we present the commissioning and the performance of the prototype in our beam test carried at DESY in June 2017.
}

@@

Future accelerator based particle physics experiments
require very precise and detailed reconstruction of the final states produced
in the beam collisions. A particular example is the next generation of $e^{+}e^{-}$
linear colliders such the ILC\cite{Behnke:2013xla,Baer:2013cma,Adolphsen:2013jya,Adolphsen:2013kya,Behnke:2013lya}.
This project will provide collisions of polarized beams with center-of-mass energies ($c.m.e$) of 250 GeV - 1 TeV.
These collisions will be studied by two multipurpose detectors:
the International Large Detector (ILD) and the Silicon Detector (SiD)\cite{Behnke:2013lya}.
To meet the precision levels required by the ILC %or CLIC
physics goals,
new techniques relying on single particle separation to make possible the choice of the best information available
in the full detector to measure the energy of the final state objects have been developed.
These techniques are called Particle Flow (PF) techniques \cite{Brient:2002gh,Morgunov:2004ed,Sefkow:2015hna}
and allow to reduce the impact of the poor resolution of the calorimeter systems (compared with trackers) in the overall reconstruction.
The PF algorithms impose some special requirements in the design of the detectors.
For example, it requires highly granular, compact
and hermetic calorimeters.

The CALICE collaboration is driving most of the efforts on R\&D of highly granular calorimeters \cite{Sefkow:2015hna} 
for future linear colliders by investigating and building prototypes for several
calorimeter concepts. One of these calorimeters 
is the silicon-tungsten electromagnetic calorimeter, SiW-ECAL.
The SiW-ECAL is the baseline choice for the ILD electromagnetic calorimeter.
It consists of a detector (in the barrel region) of 24 $X_{0}$ of thickness which corresponds to $\sim 1~\lambda_{I}$ (interaction length).
It has silicon (Si) as active material and tungsten (W) as absorber material.
The combination of Si and W choices  makes possible the design and construction
of a very compact calorimeter with highly granular and compact active layers.
It will be built an alveolar structure of carbon fiber into which modules made of tungsten
plates and the active sensors will be inserted. The very-front-end (VFE) electronics will be
embedded in the detector units. The silicon sensors will be segmented
in squared cells (or channels) of 5x5 mm: a total of $\sim 100$ million readout channels will constitute the ECAL for ILD.
The desired signal dynamic range in each channel goes from 0.5 MIP to 3000 MIPs, where the MIP acronym stands 
for the energy deposited by a minimum-inonizing-particle.
To reduce overall power consumption, the SiW-ECAL will exploit the special bunch structure
foreseen for the ILC: the $e^{+}e^{-}$ bunches trains will arrive in spills
of $\sim$ 1-2 ms width separated by $\sim$ 200 ms. The data acquisition will be gated during these short windows and during the idle time the bias currents of the electronics will be shut down.
This technique is usually denominated power pulsing. In addition to this, to cope with the large amount of channels,
the calorimeters should work in self-trigger mode (each channel featuring an internal trigger decision chain) and zero suppression mode.

@@

The current prototype is called the SiW-ECAL technological prototype. It addresses the main technological challenges: compactness,
power consumption reduction through power pulsing and VFE inside the detector close to real ILD conditions.
It will also provide data to deeply study the PF and provide input to tune simulation programs as for example
GEANT4\cite{Agostinelli:2002hh,Allison:2006ve,Allison:2016lfl} which is widely used
in particle physics to simulate the passage of particles through matter. In this section we described in detail
the main features and characteristics of the technological prototype.

@@

Current version of the PCB is called the FEV11. It has a thickness of 1.6mm and 2.7mm
if we include on top the ASICs in its current packaging (1.1 mm thick LFBGA package).
With these characteristics, a potential density of
3800 channels/dm$^{3}$ is achievable keeping the space and
interaction length requirements of the the baseline design of the ECAL forthe ILD.
This number should be compared with
the density achieved in beam tests with the physics prototype: 1500 channels/dm$^{3}$.
With the first versions
of the technological prototype we reached similar potential density level as in
the current version but equipping only a
quarter of the ASUs surface \cite{Amjad:2014tha}.

@@

A picture showing the SiW-ECAL technological prototype setup can be seen in Figure \ref{proto}.
The current prototype consists on 7 layers of SLABs housed in a PVC and aluminum structure that can host up to 10 layers in slots separated by 15mm each.
The first six layers were placed in the first six slots and the last one was in the last slot, with respect to the beam. In the following sections, we will refer to layers number 1 to 7, where
the 1 is the closest to the beam pipe and 7 is the farthest.
This setup is used for commissioning (Section \ref{sec:commissioning}) and for the beam test
(Section \ref{sec:beamtest}). In both cases, the detector was
running in power pulsing mode.

@@

All runs dedicated to the commissioning were characterized by:
\begin{itemize}
  \item their short gating windows for the acquisition (1-2ms)
   at low repetition frequencies (1-5 Hz) to minimize the chances of having real events due to cosmic rays during the data taking and the coherent noise events due to grounding issues;
 \item and the relatively high trigger threshold values, between 2 and 0.5 MIPs.
\end{itemize}

@@

We found to different types of noisy channels. One set consists of
channels randomly distributed along the surface of every ASU and the other consists
of channels located in specific areas and systematically noisy in all the ASUs. Preliminary inspections of the PCB layout
hint that the channels in the latter set may be noisy due to
improvable routing of the PCB.
Deeper studies on the PCB routing must be conducted to clarify this.
All the noisy channels have been identified and masked and the power
of their preamplifiers has been disabled. All the results shown in the following
sections are obtained in these conditions.

The list of the noisy channels was
obtained by means of dedicated data taking runs. In these runs
we scan trigger thresholds and progressively mask channels that exhibit counts. 
In each step, the decision of tagging a channel as noisy was taking following the next rules:

@@

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
  \includegraphics[width=4in]{../figs/commissioning/masked_layer.eps} \\
  \includegraphics[width=4in]{../figs/commissioning/masked_chip.eps}
  \end{tabular}
\caption{Fraction of channels that are tagged as noisy in all slabs. 
Top: different type of noisy channels per slab. 
Bottom: break down of the total number of noisy channels per ASIC. 
The ASICs 4-7 (wafer issue) and 10 from layer 1 and the ASIC 4 from layer 7 are not included
in the second plot since they are fully masked.}
\label{noisycells}
\end{figure}

@@

After the noisy channels have been masked, dedicated trigger threshold
scan run are taken, and the results are shown in threshold scan curves where the
x-axis represents the threshold value and the y-axis
the number of recorded signals normalized to 1. The threshold values are given in internal DAC units
which are translated to meaningful physical quantities in Section \ref{sec:comm_trigger_sn}.
In the absence of external signals (cosmic rays, injected signals, etc) 
the falling edge position in the threshold scan curves
is due to the electronic noise
at the output of the fast shaper (the trigger decision branch on the SKIROC)
and it depends on the slow clock frequency.
These threshold scan curves are approximated by a complementary error function:

\begin{equation}
\frac{2p_{0}}{\sqrt(\pi)} \int_{\frac{DAC-p_{1}}{p_{2}}}^{\infty} e^{-t^{2}} dt,
\label{eq_S-curve}
\end{equation}
where $p_{0}$ is 1/2 of the normalization, $p_{1}$ is the value in which the noise levels are 
the 50\% of its maximum and $p_{2}$ give us the width of the threshold scan curve.

@@

For every ASICs, after performing the fit of the theoretical curves
to the threshold scans, the average values of the   $p_{1}$ and $p_{2}$ are calculated.
These are represented by $<p_{1,2}^{ASIC}>$ in the following.
The final threshold value of every ASIC, in DAC units, was chosen 
using the following formula
\begin{equation}
Threshold{optimal}^{ASIC} =maximum(<p_{1}^{ASIC}> + 5 \times <p_{2}^{ASIC}>,230).
\end{equation}
This formula was applied 
if at least the the 30\% of the 64 channels in the ASIC could be fitted.
If not, a global threshold value of 250 was set.

@@

\begin{figure}[!t]
    \centering
  \begin{tabular}{l}
	\includegraphics[width=4in]{../figs/commissioning/scurve_pp_fastshaper_ch_DAC.eps} \\
	\end{tabular}
\caption{Threshold scan curves with charge injection (1 MIP in blue and 2 MIPs in red) for two different channels in a SKIROC2 testboard.}
\label{scurves_injection}
\end{figure}

@@

Using this new procedure we manage to reduce the number of masked channels by a factor of two
without any loss of performance, at least in the laboratory and using 3 of the 7 SLABs.
This new procedure will also be applied in the next beam test.
Also, in order to
optimize the commissioning of the detector,
we propose a new set of measurements in the next beam test such as
a threshold scan for the determination of the S/N in the trigger line. The later
can be done by the comparison of threshold curves taken with incident MIP-acting particles
and MIP-acting particles traversing the detector tilted by 45 degrees with respect to the beam direction.

\section{Performance in a beam test with positrons at DESY}
\label{sec:beamtest}

The beam line at DESY provides continuous positron beams in the energy range of 1 to 6 GeV with
rates from a few hundreds of Hz to a few KHz with a maximum of $\sim 3$ KHz for 2-3 GeV. 
In addition, DESY gives access to a bore 1 T solenoid, the PCMag.

@@

\begin{enumerate}
\item Calibration without tungsten absorber using 3 GeV positrons acting MIPs directed to 81 position equally distributed over the modules.
\item Test in magnetic field up to 1 T using the PCMag. For this test a special PVC structure was
  designed and produced to support one single SLAB.	
  The purpose of such test was twofold: first to prove that the DAQ, all electronic devices and the 
  mechanical consistency of the SLAB itself are able
  to handle strong magnetic fields; 
  second to check the quality of the data and the performance of the detector during the data taking when running
  in a magnetic field. 
  \item Response to electrons of different energies with fully equipped detector, i.e. sensitive parts {\it and} W absorber, with three different repartitions of the absorber material:
  \begin{itemize}
  \item W-configuration 1: $0.6,1.2,1.8,2.4,3.6,4.8$ and $6.6~X_{0}$
  \item W-configuration 2: $1.2,1.8,2.4,3.6,4.8,6.6$ and $8.4~X_{0}$
  \item W-configuration 3: $1.8,2.4,3.6,4.8,6.6,8.4$ and $10.2~X_{0}$
  \end{itemize}
\end{enumerate}

First reports on this beam test can be find in
Refs. \cite{Irles:2018uum,Irles:2018hcd}. These results have extended and
are discussed in the following sections. In Section \ref{sec:calib} we discuss in detail
the results of the pedestal, noise and MIP calibration.
We show also results on the pedestal and noise stability when running inside
a magnetic field in Section \ref{sec:magnetic} and in electromagnetic shower
events in Section \ref{sec:showers}. The study of the calibration of the prototype
in electromagnetic shower events is due to a future publication.

\subsection{Noise studies and MIP calibration}
\label{sec:calib}

In Figure \ref{signal_pedestal} we show the signal and pedestal distribution of a single channel after
subtracting the pedestal mean position. The results of the MIP calibration fit are shown in red.
The signal distribution is integrated over all SCAs.
For cosmetic reasons the pedestal distribution is shown only for the first SCA.

%\subsubsection{Pedestal and noise determination}
%\label{sec:pedestal}

\begin{figure}[!ht]
  \centering
  \begin{tabular}{l}
    \includegraphics[width=4in]{../figs/mip_pedestal_example.eps}
  \end{tabular}
  \caption{Pedestal (blue dashed line) and signal (black continuous line) distribution for one channel in the third layer.}
\label{signal_pedestal}
\end{figure}

The pedestal is calculated as the mean position of
the distribution of the ADC values for all channels without trigger. The noise is
associated to the width of the distribution.
The pedestal correction is done layer-, chip-, channel- and SCA-wise due to the large spread of values between pedestals, as observed in 
Figure \ref{pedestal_layer} (left plot) and Figure \ref{pedestal_all} (also left plot).
For the noise, the dispersion is much smaller ($\sim 5 \%$). This is shown in the right plots of Figures \ref{pedestal_layer} and \ref{pedestal_all}.
From now on, the pedestal correction is applied to all the results presented.
The resulting spectra are fit by
a Landau function convoluted with a Gaussian.
The most-probable-value of the convoluted function is taken as the MIP value, allowing thus for a direct
conversion from ADC units to energy in MIP units.
The fit succeeded in 98\% of the cases and the spread of the resulting MPV is 5\%.
The remaining channels will be discarded. Results are summarized in figure \ref{mipandSN}, leftmost plot.

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
    \includegraphics[width=2.8in]{../figs/pedestal/ped_mean_layer2.eps} & \includegraphics[width=2.8in]{../figs/pedestal/width_mean_layer2.eps}
  \end{tabular}
  \caption{Pedestal mean position (left plot) and width (right plot) for all channels in one layer.}
\label{pedestal_layer}
\end{figure}

@@

@@

As a sumamry Figure \ref{mip3peaks} shows the response of all channels integrated over the calibration run.
This plot is obtained after further refinement of the sample by selecting incident tracks.
The maximum peaks at 1 MIP as expected after a good calibration.
In addition to this, a second and a third peaks
are visible as shoulders. These shoulder are associated to 
events involving multiple 
particles crossing the detector.

\begin{figure}[!t]
  \centering 
    \begin{tabular}{ll}
      \includegraphics[width=4in]{../figs/MIP/MIP3peaks.eps} 
    \end{tabular}
    \caption{Energy distribution for all calibrated channels when selecting incident tracks of 3 GeV positron acting as MIPs.}
\label{mip3peaks}
\end{figure}

To evaluate 
the single hit detection efficiency we define a high purity sample of
events by selecting
tracks with at least 4 layers with a hit in exactly the same channel. Afterwards we 
check which layers have or not a hit in the same or in the closest neighboring channels with energy larger or equal than 0.3 MIP.
We repeat this procedure for all channels.
The results are shown in Figure \ref{efficiency}. Except few exceptions, the efficiency is 
compatible with $100\%$.
Lower efficiencies in the first layer are related to the presence of
noisy channels not spotted during the commissioning. In the last layer we also observe few small deviations
which are associated to the outliers channels, hinting for a small misalignment of the last layer.

\begin{figure}[!t]
  \centering 
   % \begin{tabular}{ll}
  \includegraphics[width=4in]{../figs/MIP/efficiency_nhits4_chips.eps}
  %& \includegraphics[width=2.8in]{../figs/MIP/efficiency_nhits4_chips_zoom.eps} \\
  %  \end{tabular}
  \caption{MIP detection efficiency for all layers and ASICs in high purity samples of tracks of MIP-like acting particles.}
\label{efficiency}
\end{figure}

@@

The signal-over-noise ratio in the charge measurement (corresponding to the slow shaper of the SKIROC2) is defined 
as the ratio between the most-probable-value of
the Landau-gauss function fit to the data (pedestal subtracted) and the noise (the pedestal width). This quantity 
has been calculated for all channels and all layers. 
Results are summarized in Figure \ref{mipandSN}, rightmost plot.

@@

The data taking inside the magnetic field has been divided in three runs:
\begin{enumerate}
\item a with a magnetic field of 1 T;
\item a run with 0.5 T;
\item and a final run with the magnet off.
\end{enumerate}

The beam, 3 GeV positrons, was directed in the area of the PCB readout by the ASIC number 12.
The pedestal positions and noise levels of the channels of the ASIC 12 when the
SLAB is inside of the PCMag are compared with the results from the calibration run described in the previous section.
This is shown in Figure \ref{pedestal_magnetic}.
We see that the agreement is perfectly good within the statistical uncertainties.
Due to the lower rates in this beam area, the
analysis is only done up to few SCAs.

@@

In this section we discuss the pedestal stability in events with large amount of charge collected by the ASICs, as are the 
electromagnetic shower events. All the results shown in this section correspond to data taken during the tungsten program, 
using the W-configuration number 2 when shooting the beam in the area registered by the ASIC 12 (and partially in the 13). 
For simplicity, only information recorded by ASIC 12 will be shown. 
In order to select a high purity of
electromagnetic shower like the events, 
we used a simple criteria: select only events with at least 6 of the layers with at least a hit with E > 0.5 MIP.

\begin{figure}[!ht]
  \centering 
    \begin{tabular}{ll}
      \includegraphics[width=2.8in]{../figs/pedestal/pedestal_vs_energy_shower.eps} & \includegraphics[width=2.8in]{../figs/pedestal/pedestal_vs_nhits_shower.eps} \\
    \end{tabular}
    \caption{Left: mean position of the projection of the pedestal distribution of all channels
      calculated when different energies are collected in the ASIC (in bins of 10 MIPs).
      Right: same but as a function of the number of hits. In both cases, the results are shown for few SCA.
      The points for the curves with SCA different than zero are slightly shifted in the x-axis to optimize the visualization.}
\label{pedestal_shower_1}
\end{figure}
